---
title: "Week 1 Activity"  
author: "NAME"
format: html
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: true
  error: false
---

Run this code chunk before you start each session. You do not yet need to understand it.
```{r}
#| label: setup

library(tidyverse)
library(mosaic)
library(ggformula)
```


## Activity: king data set

Read in the csv file `king.csv` and store it as the object `king` by modifying the code below to fill in each blank. To fill in the blanks in this assignment ___blank___, replace the entire phrase, including underscores. After reading in your data, it is a good habit to always use the function `names()` on your dataframe object to see the names of the variables.

```{r}
#| label: import-king-data

king <- ___goal___("___file___")
names(king) # will print out the variable names
```


### 1.   

Find the mean birth weight of babies in the `king` data set.

```{r}
#| label: calculate-mean

__goal__(__formula__, data = __mydata__)
```


### 2.   

Create a table for the mothers' education level in the `king` data set.

```{r}
#| label: calculate-table

__goal__(__formula__, data = __mydata__)
```


### 3.  

Find the correlation between birth weight and estimated gestational age.

```{r}
#| label: calculate-correlation

__goal__(__formula__, data = __mydata__)
```



