---
title: "STAT 250D Week 6 Activity"
author: "NAMES"
format: html
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: true
  error: false
---


## Intro to QQ Plots

Read in any necessary packages by replacing the __hint__ below.

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(__graphics package__)
library(__stats package__)
```


### Generic code structure

The following code will produce a QQ plot with the 1:1 line. The formula will depend on whether you are assessing normality for a two independent sample or for matched pairs data.

For two independent sample:

`~y|x` where y is the numeric response variable and x is the categorical explanatory variable.

For matched pairs:

`~(x1-x2)` where x1 and x2 are both numeric responses for the categories 1 and 2.


This is the generic code and the pieces that are filled in for each. (This is not a question to edit, or a code to run, just one to read, understand, and refer to.)
```{r eval = FALSE}
gf_qq([formula], data = [dataframe_name]) |> 
  gf_qqline()
```



### Sample from a normal population

Run the following code to produce a QQ plot for a random sample of values taken from a normal population distribution. You do not need to learn or understand the code other than what makes the qqplot. 


```{r}
n <- 50  # set the sample size
mu <- 100  # set the population mean
sigma <- 5  # set the population sd

x <- rnorm(n, mu, sigma) # take a random sample from a normal population with parameters set above

gf_qq(~x, xlab = "Theoretical Z-Score", ylab = "Sample Data") |>
  gf_qqline()
```


Run the code chunk again a few more times. What do you notice?

> Insert answer here.


Change the sample size to 100 and run the code multiple times. What do you notice?

> Insert answer here.


Each time you run the code chunk, a new sample is taken from the normal population distribution and the new sample's QQ plot is produced. The deviations you see are what you can expect to see for a given sample size taken from the normal distribution.



### Sample from a non-normal population

Now, let's look at a non-normal population, with the same sample size as you ran last above. Run the following code a few times. What do you notice?

```{r}
z <- rgamma(n, 1)
gf_qq(~z, xlab = "Theoretical Z-Score", ylab = "Sample Data") |>
  gf_qqline()
```


> Insert answer here.






