---
title: "Week 2 Activity"  
author: "NAME"
format: html
embed-resources: true
html-math-method: mathml
execute: 
  warning: false
  echo: true
  error: true
---

Run this code chunk before you start each session.  
```{r}
#| label: setup

library(tidyverse)
library(mosaic) # package for statistics functions
library(ggformula) # package for graphics functions
```


## Activity: Exploratory Data Analysis  

### King County data  

Recall the King data set that represents a sample of babies born in 2001 in King County, Washington. We are going to explore the following research question:  

*On average, did women in King County, Washington with different educational levels have babies with different birth weights in 2001?*  


Read in the `king.csv` data set and print the variable names.  

```{r}
king <- ___goal___("___filename___")
___goal___(penguins)


# This line of code reorders education levels as low, middle, high - you DO NOT yet need to understand until later in the semester
king <- mutate(king, educlv = factor(educlv, levels=c("Low","Middle","High")))
```


### 1.  

Create a histogram that addresses the question, being sure to use good graphic practices.

< Insert code chunk >


### 2.  

Calculate summary statistics of birth weight for each education level. 

< Insert code chunk >


### 3.  

Describe the shape of each distribution. Based on the shape, how do you expect the mean and median birth weight to compare for each education level? Why?

> Insert answer here 


### 4.  

Compare the mean and median birth weight for each education level. If any, how large are the differences between the mean and median? Are these differences meaningful?

> Insert answer here


### 5.    

Determine if there are any outliers of birth weight for mothers with *high* education levels. If so, how many are there? Are they unusually large or unusually small birth weights? How do you know? 

< Insert code chunk >

> Insert answer here





